\PaperTitle

### 2024-05-05 Final_Report/paper.tex

As you can see from the scatter plot in figure \ref{fig:log_reg_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results. We'll get into the specifics of the time variable's specific limitations shortly.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{Figures_and_Graphs/ActualClassifiedPacketsScatterpng.png}
    \caption{True Classes of Test Data}
    \label{fig:actual_scatter}
\end{figure}

As you can see from the difference between the logistic regression scatterplot in figure \ref{fig:log_reg_scatter} and the actual class scatterplot in figure \ref{fig:actual_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results. We'll get into the specifics of the time variable's specific limitations shortly.
